\cvsection{Publications}


\begin{cventries}

\cventry
{}{Journal Papers}{}{} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
        \item \textbf{Chen, J.} and Wong, K. C. (2020). RNCE: Network Integration with Reciprocal Neighbors Contextual Encoding for Multi-modal Drug Community Study. (Submitted Paper.)
        \item \textbf{Chen, J.} and Wong, K. C. (2020). Categorical Matrix Completion with Active Learning for High-throughput Screening. IEEE/ACM transactions on computational biology and bioinformatics.
        \item Zhao, J., Hinton, P., \textbf{Chen, J.}, \& Jiang, J. (2020). Causal inference for the effect of environmental chemicals on chronic kidney disease. Computational and Structural Biotechnology Journal, 18, 93-99.
        \item Wong, K. C., \textbf{Chen, J.}, Zhang, J., Lin, J., Yan, S., Zhang, S., ... \& Kwong, S. (2019). Early Cancer Detection from Multianalyte Blood Test Results. iScience, 15, 332-341.
        \item \textbf{Chen, J.}, Yan, S., \& Wong, K. C. (2018). Verbal aggression detection on Twitter comments: Convolutional neural network for short-text sentiment analysis. Neural Computing and Applications, 1-10.      
    \end{cvitems}
}

\cventry
{}{Conference Papers}{}{} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
        \item \textbf{Chen, J.}, Yan, S., \& Wong, K. C. (2017, March). Aggressivity detection on social network comments. In Proceedings of the 2017 International Conference on Intelligent Systems, Metaheuristics \& Swarm Intelligence (pp. 103-107).   
    \end{cvitems}
}
\cventry
{}{Book Chapters}{}{} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
        \item \textbf{Chen, J.} and Wong, K. C. (2020). Analyzing High-order Epistasis from Genotype-Phenotype Maps using 'Epistasis' Package. Epistasis in Methods in Molecular Biology.
    \end{cvitems}
}
\end{cventries}
